Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-06-02 doc/manuscript/manuscript.Rmd
Added to manuscript

Models were fit using the gamem_met function from the metan package[@olivotoMetanPackageMultienvironment2020]. Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R. The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means for all collected phenotypes. Pearson correlation coefficients between each phenotype were calculated with the metan package.

@@

## Phenotypic correlations
A strong negative correlation was observed in both tests between seed protein and seed oil content. A coefficient of r = -0.93 was observed in both populations. A negative correlation was observed between seed protein and yield with correlation coefficient of r = -0.29 was observed in both tests. This correlation was not statistically significant in either population. A weak positive correlation was observed between seed oil and seed yield in both populations. A correlation coefficient of r = 0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed in Test 2. These correlation coefficients were not statistically significant in either population.

@@

@@

Among these genotypes are several with both average seed protein and average seed yield that were greater than the averages of the checks for each test. These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs N18-1761 and N18-1627 from test 2. Of particular note are genotypes N18-1632-1 from test 1 and N18-1761 from test 2. On average, genotype N18-1632-1 had a protein content that was 113.9% of the check average while maintaining a yield average that was 101.5% that of the check average. SImilarly, RIL N18-1761 from test 2 had a protein

```{=tex}
\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}
```

>>>>

Models were fit using the gamem_met function from the metan package[@olivotoMetanPackageMultienvironment2020]. Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R. The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL phenotype means to check means for all collected phenotypes. A sidak adjustment was used to account for multiple comparisons in the calculation of contrasts.

Pearson correlation coefficients between each phenotype were calculated with the metan package.

@@

## Phenotypic correlations
A strong negative correlation was observed in both tests between seed protein and seed oil content. A coefficient of r = -0.93 was observed in both populations. A negative correlation was observed between seed protein and yield with correlation coefficient of r = -0.29 was observed in both tests. This correlation was not statistically significant in either population. A weak positive correlation was observed between seed oil and seed yield in both populations. A correlation coefficient of r = 0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed in Test 2. These correlation coefficients were not statistically significant in either population. Visualizations of the pairwise correlation coefficients for Tests 1 and 2 can be seen in supplementary figures 2 and 3, respectively.

@@

A detailed summary of all contrasts can be seen in supplementary table 1.

@@

Among these genotypes are several with both average seed protein and average seed yield that were greater than the averages of the checks for each test. These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs N18-1761 and N18-1627 from test 2. Of particular note are genotypes N18-1632-1 from test 1 and N18-1761 from test 2. On average, genotype N18-1632-1 had a protein content that was 113.9% of the check average while maintaining a yield average that was 101.5% that of the check average.

```{=tex}
\begin{figure}[H]
\centering
\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/supplemental/supplemental_figure_1.pdf}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}
```

### 2022-06-02 doc/manuscript/manuscript.tex
Added to manuscript

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL phenotype means to check means for all collected phenotypes.
Pearson correlation coefficients between each phenotype were calculated
with the metan package.

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

A strong negative correlation was observed in both tests between seed
protein and seed oil content. A coefficient of r = -0.93 was observed in
both populations. A negative correlation was observed between seed
protein and yield with correlation coefficient of r = -0.29 was observed
in both tests. This correlation was not statistically significant in
either population. A weak positive correlation was observed between seed
oil and seed yield in both populations. A correlation coefficient of r =
0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed
in Test 2. These correlation coefficients were not statistically
significant in either population.

@@

Several RILs in each of the tests had yield that was comparable to that
of their check cultivars. This was determined both quanititatively
through the use of contrasts between the mean of each RIL with the
average of the yield check means, and qualitatively by inspecting the
standard errors on the estimation of the genotype marginal means for
yield. No genotypes had yield that was quantitatively higher than that
of the yield checks, however many had comparable yield. Many of these
genotypes with comparable yield also had protein content that was
superior to the check average in each test. No genotypes had oil that
was superior to the check cultivars, but some had comparable yield and
oil content as well as superior protein content.

RILs were also evaluated for lodging and seed quality. All RILs had seed
quality that was on par with that of the high-yielding checks however,
however 11 genotypes had lodging scores that were significantly greater
than the checks on the basis of contrasts. These RILs were removed from
consideration for recommendation on the basis of their relatively poor
agronomic performance.

@@

Four genotypes had yield and oil that was similar to that of the yield
checks, and seed protein that was greater than the average of the
checks. These genotypes are N18-1635 from Test 1 and genotypes N18-1627,
N18-1643, and N18-1783 from Test 2.

@@

@@

Seventeen out of the thirty RILs had a similar yield and superior
protein content to the check cultivars.

@@

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

>>>>

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL phenotype means to check means for all collected phenotypes.
A sidak adjustment was used to account for multiple comparisons in the
calculation of contrasts.

Pearson correlation coefficients between each phenotype were calculated
with the metan package.

@@

\hypertarget{results-and-discussion}{%
\section{Results and discussion}\label{results-and-discussion}}

@@

A strong negative correlation was observed in both tests between seed
protein and seed oil content. A coefficient of r = -0.93 was observed in
both populations. A negative correlation was observed between seed
protein and yield with correlation coefficient of r = -0.29 was observed
in both tests. This correlation was not statistically significant in
either population. A weak positive correlation was observed between seed
oil and seed yield in both populations. A correlation coefficient of r =
0.24 was observed in Test 1 while a coefficient of r = 0.28 was observed
in Test 2. These correlation coefficients were not statistically
significant in either population. Visualizations of the pairwise
correlation coefficients for Tests 1 and 2 can be seen in supplementary
figures 2 and 3, respectively.

@@

Several RILs in each of the tests had yield that was comparable to that
of their check cultivars. This was determined both quantitatively
through the use of contrasts between the mean of each RIL with the
average of the yield check means, and qualitatively by inspecting the
standard errors on the estimation of the genotype marginal means for
yield. No genotypes had yield that was quantitatively higher than that
of the yield checks, however many had comparable yield. Many of these
genotypes with comparable yield also had protein content that was
superior to the check average in each test. No genotypes had oil that
was superior to the check cultivars, but some had comparable yield and
oil content as well as superior protein content.

RILs were also evaluated for lodging and seed quality. All RILs had seed
quality that was on par with that of the high-yielding checks however,
however 11 genotypes had lodging scores that were statistically
significantly greater than the checks on the basis of contrasts. These
RILs were removed from consideration for recommendation on the basis of
their relatively poor agronomic performance.

A detailed summary of all contrasts can be seen in supplementary table
1.

@@

Four genotypes had yield and oil that was similar to that of the yield
checks, and seed protein that was greater than the average of the
checks. These genotypes are N18-1635 from Test 1 and genotypes N18-1627,
N18-1643, and N18-1783 from Test 2. Summary data for these lines is
given in table 1.

@@

A strong negative correlation was observed in both populations betweeen
seed oil and seed protein. This observation matches well with previous
findings on the inverse correlation between seed protein and seed oil.
Many RILs had high protein when compared with the check cultivars so it
was not surprising that relatively few had both a superior seed protein
content, and a comparable seed oil content.

@@

Seventeen RILs had a similar yield and superior protein content to the
check cultivars. Summary data for the seed protein and seed yield of
these lines is given in table 2. The maximum yielding line

@@

Among these genotypes are several with both average seed protein and
average seed yield that were greater than the averages of the checks for
each test. These N18-1632-1, N18-1620, N18-1635 from test 1 and RILs
N18-1761 and N18-1627 from test 2. Of particular note are genotypes
N18-1632-1 from test 1 and N18-1761 from test 2. On average, genotype
N18-1632-1 had a protein content that was 113.9\% of the check average
while maintaining a yield average that was 101.5\% that of the check
average.

\begin{figure}[H]
\centering
\includegraphics[width=15 cm]{C:/Users/Jay/Documents/R/Projects/Jay_yield/exports/plots/supplemental/supplemental_figure_1.pdf}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest.}
